Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-11 paper/virtual_cytoplasm_v2.tex
Small technical cleanups

\title{Cytoplasm Simulation}

\author{Zahedeh}
\affiliation{Science for Life Laboratory, Department of Cell and Molecular Biology. Uppsala University, SE-751 05 Uppsala, Sweden}

\author{Leandro Oliveira Bortot}
\affiliation{Laboratory of Biological Physics, School of Pharmaceutical Sciences of Ribeirão Preto, University of São Paulo, Ribeirão Preto, Brazil}

\author{David van der Spoel}
\affiliation{Science for Life Laboratory, Department of Cell and Molecular Biology. Uppsala University, SE-751 05 Uppsala, Sweden}
\email{aaa@aaa.com}

@@

\begin{figure}
\includegraphics[scale=0.6]{diff_singles.pdf} &
\includegraphics[scale=0.6]{diff_cyto.pdf} &
\includegraphics[scale=0.6]{diff_cyto_over_singles.pdf}
\caption{A) Diffusion coefficient of crowders from single molecule simulations.  B) Diffusion coefficient of crowders from cytoplasm simulations. C) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis.}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{rmsf.pdf}
\caption{Root mean squared fluctuations of 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues of each chain of crowders.}
\end{figure}

@@

\bibliography{../bibtex/library}

>>>>

\title{Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm}

\author{Zahedeh Bashardanesh}
\affiliation{Science for Life Laboratory, Department of Cell and Molecular Biology. Uppsala University, SE-751 05 Uppsala, Sweden}

\author{Leandro Oliveira Bortot}
\affiliation{Laboratory of Biological Physics, School of Pharmaceutical Sciences of Ribeir{\~a}o Preto, University of S{\~a}o Paulo, Ribeir{\~a}o Preto, Brazil}

\author{David van der Spoel}
\affiliation{Science for Life Laboratory, Department of Cell and Molecular Biology. Uppsala University, SE-751 05 Uppsala, Sweden}
\email{david.vanderspoel@icm.uu.se}

@@

\begin{figure}
\includegraphics[scale=0.5]{diff_singles.pdf} \\
\includegraphics[scale=0.5]{diff_cyto.pdf} \\
\includegraphics[scale=0.5]{diff_cyto_over_singles.pdf}
\caption{A) Diffusion coefficient of crowders from single molecule simulations.  B) Diffusion coefficient of crowders from cytoplasm simulations. C) The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{rmsf.pdf}
\caption{Root mean squared fluctuations of 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues of each chain of crowders.}
\end{figure}

@@

\bibliography{library}
